Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-11-27 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
reformulations on first part of related work section

\section{Related Work}
\label{sec:literature}
In this section, we review some of the most related work using data mining approaches employed to solve scheduling problems. Over the last decades, solving the scheduling problem has attracted the interest of many researchers. The main idea of data mining in these applications is to explore the patterns from the obtained solutions by some heuristics and then develop decision rules that approximate the order of the operations in each machine \cite{ismail2012production}. More precisely, it aims to get an order of all operations in the given instance according to their characteristics.

Data mining methodologies were applied to explore the patterns in data generated by genetic algorithms in \cite{koonce2000using}. This work aimed to generate rules determining the priority for each job. The authors solved the scheduling problem using a genetic algorithm and derived dispatching rules that considered characteristics like the rank of operations, processing time, machine load, and remaining processing time. The evaluation of the obtained rules was done on previously unused random instances. Obtained results show that the generated rules were able to outperform the shortest processing time heuristic. One of the drawbacks is that the problem instances considered contain only 36 operations, i.e., considered JSP instances were relatively small.

The authors in \cite{harrath2002genetic} also implemented a genetic algorithm to construct and analyze solutions of JSP instances for the feature extraction for the suggested dispatching rule. In particular, the approach uses processing time, job length, remaining processing time, the rank of the operation, and machine load. The authors preprocessed the data by converting it from quantitative into qualitative representation, which was then used to build a generic model for scheduling problems as follows: First, the authors sorted the operations share the same machine according to processing time. Then, if two or more operations have the same processing time, the heuristic preferred a job with the smallest length. Finally, if the jobs have the same length, the remaining processing time heuristic was used as a tie-breaker. In opposite, our approach does not depend on a set of features extracted from an instance. New features can easily be included in the set of observations and considered by the clustering method.

In addition to the work focusing on static JSP, there are approaches using data mining methods for dynamic JSP. For instance, \cite{shahzad2010discovering} presents new dispatching rules for JSP aiming to minimize makespan and which process a given JSP instance as follows: 
First, a scheduling instance is solved using Tabu Search and the obtained solutions are used as a training set to get a rule-set capable of approximating efficient solutions. This approach considers features like EST, the difference in remaining processing time for a job, and the difference in the processing time of two operations, to create a rule-set for dispatching the operations. The experiments showed that the results of mined rule-set are superior or comparable to the heuristics in the literature.

The variable neighborhood search (VNS) is combined with the k-Means algorithm to address Dynamic JSP \cite{adibi2014clustering}. The proposed algorithm depends on extracting information from the problem's input data when an event, like a machine breakdown or an addition of a new job, occurs. At any rescheduling point, cluster analysis is performed to replace jobs according to their distances. In other words, a job that belongs to a farther cluster has a greater probability to be selected in making a new adjacent than the other belonging to a closer cluster. The proposed method was compared to VNS and some common heuristics using a simulated job shop. the results indicated that the performance of the proposed model is better than the others, including heuristics like FIFO, LIFO, and SPT.

>>>>

\section{Related Work}
\label{sec:literature}

Data mining approaches~\cite{ismail2012production} have been extensively proposed and studied to generate % so-called
dispatching rules~\cite{blackstone1982state} for scheduling problems.
Unlike combinatorial and stochastic optimization methods, dispatching rules do not take
complete schedules into account, but address the prioritization of operations for making
local allocation decisions by greedy scheduling algorithms.
In addition to Earliest Starting Time (EST), First-In-First-Out (FIFO), and
Most Total Work Remaining (MTWR), which we also use for obtaining starting times as features,
common dispatching rules include Last-In-First-Out (LIFO) and policies incorporating
Job Length (JL) in terms of the number of operations as well as further features
like those described in Section~\ref{sec:features}:
Operation Position (OP), Processing Time (PT), Remaining Processing Time (RPT), 
Time Length of a Job (TLJ), and Machine Load (ML).
While dispatching rules enable an efficient operation allocation,
even under real-time conditions, the quality of their decisions heavily depends on the
problem instances under consideration, where data mining techniques come in to
improve over tedious and ad hoc manual tuning.

The approach of~\cite{koonce2000using} incorporates data mining methods,
using OP, PT, RPT, and ML as features, for generating dispatching rules that approximate
operation priorities found in schedules optimized by means of a genetic algorithm.
On randomly generated test instances of comparably small size, i.e., $36$ operations
per instance, the generated dispatching rules were shown to outperform greedy search
with shortest PT as a rigid criterion for making allocation decisions.
Genetic algorithms are also utilized in~\cite{harrath2002genetic} to obtain
promising solutions for JSP instance and extract features to consider for the
construction of dispatching rules.
The specifically generated three-tiered policy comprises shortest PT, smallest JL, and longest RPT as
dispatching criteria in the order of significance.
Note that such a composite dispatching rule needs to reconstructed from scratch when
new features or problem instances are analyzed, while our constrained clustering method
can readily be applied to different instance or feature sets, respectively.

Beyond static scheduling, dynamic JSP~\cite{french82a} deals with events, such as 
the release of new jobs or sudden machine breakdowns, along with rescheduling or
updating dispatching rules, respectively.
In analogy to static approaches,
the processing method of~\cite{shahzad2010discovering} applies tabu search to
training instances and generates allocation policies approximating the optimized
complete schedules based on features like EST, PT, and RPT of operations.
Applied in the dynamic JSP setting, the dispatching rules obtained by means of data mining
were shown to yield better or comparable performance to rigid allocation strategies from the
literature.
A rescheduling approach combining Variable Neighborhood Search (VNS)
with K-Means clustering is presented in~\cite{adibi2014clustering},
where clusters are updated to reconfigure the VNS on each event.
The performance of this combined rescheduling strategy in the dynamic JSP setting turned out
to be better than pure VNS and greedy algorithms with the FIFO, LIFO, or
shortest PT allocation policy.

% In this section, we review some of the most related work using data mining approaches employed to solve scheduling problems. Over the last decades, solving the scheduling problem has attracted the interest of many researchers. The main idea of data mining in these applications is to explore the patterns from the obtained solutions by some heuristics and then develop decision rules that approximate the order of the operations in each machine \cite{ismail2012production}. More precisely, it aims to get an order of all operations in the given instance according to their characteristics.

% Data mining methodologies were applied to explore the patterns in data generated by genetic algorithms in \cite{koonce2000using}. This work aimed to generate rules determining the priority for each job. The authors solved the scheduling problem using a genetic algorithm and derived dispatching rules that considered characteristics like the rank of operations, processing time, machine load, and remaining processing time. The evaluation of the obtained rules was done on previously unused random instances. Obtained results show that the generated rules were able to outperform the shortest processing time heuristic. One of the drawbacks is that the problem instances considered contain only 36 operations, i.e., considered JSP instances were relatively small.

% The authors in \cite{harrath2002genetic} also implemented a genetic algorithm to construct and analyze solutions of JSP instances for the feature extraction for the suggested dispatching rule. In particular, the approach uses processing time, job length, remaining processing time, the rank of the operation, and machine load. The authors preprocessed the data by converting it from quantitative into qualitative representation, which was then used to build a generic model for scheduling problems as follows: First, the authors sorted the operations share the same machine according to processing time. Then, if two or more operations have the same processing time, the heuristic preferred a job with the smallest length. Finally, if the jobs have the same length, the remaining processing time heuristic was used as a tie-breaker. In opposite, our approach does not depend on a set of features extracted from an instance. New features can easily be included in the set of observations and considered by the clustering method.

% In addition to the work focusing on static JSP, there are approaches using data mining methods for dynamic JSP. For instance, \cite{shahzad2010discovering} presents new dispatching rules for JSP aiming to minimize makespan and which process a given JSP instance as follows: 
% First, a scheduling instance is solved using Tabu Search and the obtained solutions are used as a training set to get a rule-set capable of approximating efficient solutions. This approach considers features like EST, the difference in remaining processing time for a job, and the difference in the processing time of two operations, to create a rule-set for dispatching the operations. The experiments showed that the results of mined rule-set are superior or comparable to the heuristics in the literature.

% The variable neighborhood search (VNS) is combined with the k-Means algorithm to address Dynamic JSP \cite{adibi2014clustering}. The proposed algorithm depends on extracting information from the problem's input data when an event, like a machine breakdown or an addition of a new job, occurs. At any rescheduling point, cluster analysis is performed to replace jobs according to their distances. In other words, a job that belongs to a farther cluster has a greater probability to be selected in making a new adjacent than the other belonging to a closer cluster. The proposed method was compared to VNS and some common heuristics using a simulated job shop. the results indicated that the performance of the proposed model is better than the others, including heuristics like FIFO, LIFO, and SPT.
